\sys: Automated Data-Parallel Shell Processing

### 2020-04-14 pldi/draft.tex
Add a comment in the PLDI draft

\TODO{Problem: Cat (and other commands that have multiple inputs) is
  not eager. Illustration: Show a parallel pipeline having a cat that
  gathers input somewhere (and a sort merge maybe). The way pipes
  work, this graph will essentially evaluate almost completely
  sequentially. Maybe go through the steps that cat asks for the first
  line of its first input until ithe first input is done and then goes
  to the second. This leads to processor under-utilization. Solution:
  We add eager nodes that eagerly consume all their input (even if
  their output does not ask for it). Eager nodes are themselves part
  of the dataflow graph (and model) and essentially perform an
  identity function. This makes all processors as utilized as possible
  and for CPU heavy tasks it leads to speedup. For IO heavy (and CPU
  light) tasks it has some overhead. We evaluate eager in section X
  (We should also say something about a CPU light task).}

@@

\begin{figure*}[t]
    \centering
    %% \subcaptionbox{\label{eval:minimal_grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:minimal_sort}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:topn}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:wf}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:spell}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \caption{a}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/spell_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Three different configurations per benchmark:
      (i) parallel, focusing only on the parallel execution,
      (ii) +compile, adding \sys' pre-processing overheads, and
      (iii) \kk{Add with , without eager and split here}.
      \nv{Candidate values, based on the HW we have 2, 4, 8, 16, 32, 64. Also, maybe it makes sense to show log x-axis?}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

>>>>

\TODO{Problem: Cat (and other commands that have multiple inputs) is
  not eager. Illustration: Show a parallel pipeline having a cat that
  gathers input somewhere (and a sort merge maybe). The way pipes
  work, this graph will essentially evaluate almost completely
  sequentially. Maybe go through the steps that cat asks for the first
  line of its first input until ithe first input is done and then goes
  to the second. This leads to processor under-utilization. Solution:
  We add eager nodes that eagerly consume all their input (even if
  their output does not ask for it). Eager nodes are themselves part
  of the dataflow graph (and model) and essentially perform an
  identity function. This makes all processors as utilized as possible
  and for CPU heavy tasks it leads to speedup. For IO heavy (and CPU
  light) tasks it has some overhead. We evaluate eager in section X
  (We should also say something about a CPU light task). A good thing
  is that they work for all possible commands with almost no overhead,
  without having to make each specific command eager.}

@@

\begin{figure*}[t]
    \centering
    %% \subcaptionbox{\label{eval:minimal_grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:minimal_sort}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:topn}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:wf}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:spell}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \caption{a}
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/spell_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/set-diff_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%

    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/alt_bigrams_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Three different configurations per benchmark:
      (i) parallel, focusing only on the parallel execution,
      (ii) +compile, adding \sys' pre-processing overheads, and
      (iii) \kk{Add with , without eager and split here}.
      \nv{Candidate values, based on the HW we have 2, 4, 8, 16, 32, 64. Also, maybe it makes sense to show log x-axis?}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}
